diffusion, websites with 1 pc

### 2022-06-01 src/level_lisa_la.Rmd
updates

library(tidyverse)
library(rprojroot)
library(rgdal)
library(rgeos)
library(spdep)
library(tmap)
library(maptools)
library(knitr)
library(REAT)
library(tidygeocoder)
library(geosphere)
library(broom)

@@

@@

>>>>

library(tidyverse)
library(rprojroot)
library(rgdal)
library(rgeos)
library(spdep)
library(tmap)
library(maptools)
library(knitr)
library(REAT)
library(tidygeocoder)
library(geosphere)
library(broom)
library(foreach)

@@

## lisa maps parallel

path.out <- paste0(path, "/outputs/lisa_level_pc_test", n, "_la") # for unique PC
#path.out <- paste0(path, "/outputs/lisa_level_pc", m, "_la")  # for multiple PC

#setup cluster
#https://www.blasbenito.com/post/02_parallelizing_loops_with_r/
n.cores <- parallel::detectCores() - 1
my.cluster <- parallel::makeCluster(
  n.cores, 
  type = "PSOCK"
  )
print(my.cluster)
doParallel::registerDoParallel(cl = my.cluster)
foreach::getDoParWorkers()

#for (t in 1996:2012){
foreach(t = 1996:2012, .packages = c("tidyverse",
                                     "rgdal",
                                     "rgeos",
                                     "spdep",
                                     "tmap",
                                     "maptools",
                                     "knitr",
                                     "broom")) %dopar% {
test <- la
test@data <- test@data %>% left_join(df[df$year==t,], by = c("LAD21CD"="ladcd")) %>% 
  mutate(n = ifelse(is.na(n), 0, n),           # 0 for NAs and the same for year
         year = ifelse(is.na(year), t, year))

map <- tm_shape(mun_merge_new, projection = "+init=epsg:4326") + tm_fill(col = "quadrant", breaks = breaks, 
                                         palette = c("white","red","blue",
                                                     rgb(0,0,1,alpha=0.4),
                                                     rgb(1,0,0,alpha=0.4)), 
                                         labels = c("Not significant", "High-High","Low-Low","Low-High","High-Low"), 
                                         title="LISA for level, LA") +
  tm_legend(text.size = 1) +
  #tm_scale_bar(position = c("LEFT", "BOTTOM"),text.size = 1.0)+
  #tm_compass(type = "8star",   position = c("RIGHT", "BOTTOM"),      show.labels = 2,   text.size = 0.5)+
  #tm_borders(alpha=.1) +
  tm_borders(lwd = 0) +
  tm_shape(la, simplify = .2) + tm_borders(alpha=1, lwd = .7) +
  tm_shape(tif_sf) + tm_dots() + tm_text("name", size = .5) +
  tm_layout( frame = FALSE,  title = t) #"LISA with the R p-values ") +
tmap_options(check.and.fix = TRUE)
tmap_save(map, filename = paste(path.out, t, ".png", sep = ""))
}
```

@@

All R^2 dataframe

```{r}
path.out <- paste0(path, "/outputs/r2_all_la.csv")

r2.all <- dens.London %>% 
  rename(London.LA = rsquared) %>% 
  left_join(dens.distMet) %>% 
  rename(cities.LA = rsquared) %>% 
  left_join(dens.dist.retail) %>% 
  rename(retail.LA = rsquared) %>% 
  relocate(year, .before = London.LA) %>% 
  arrange(year)

write_csv(r2.all, path.out)
```
